Efficient Selection of Time Series Shapelets

### 2024-04-12 Docs/paper/main.tex
todos

\section{Introduction}
Time series classification is similar to traditional classification where the
difference is that the order of the values of the time series is crucial.
The order holds discriminatory features for the time series. The literature
is rich of algorithms for classification, and one way to group these
algorithms is based on the techniques that each algorithm uses to exploit the
discriminatory features suggested by Bagnall et al.~\cite{bake_off}:
\begin{itemize}
	\item Distance based: Classification is based on using distance measures to
	      the raw time series.
	\item Feature based: Global features are extracted and the data is transformed
	      from the time domain to the feature domain spanned by the extracted
	      features, and the classification is done using a standard classifier.
	\item Interval based: Techniques in this family extract one or more intervals,
	      then statistical summaries of these intervals are used as features.
	\item Shapelet based: This technique exploits discriminatory patterns that
	      appear in time series of the same class.
	\item Dictionary based: These algorithms use as features the count of
	      repeating patterns.
	\item Convolution based: Features used are extracted from time series using
	      convolutions and pooling operations.
	\item Deep learning: Classification is done by feeding the data to neural
	      networks
	\item Hybrid: Algorithms in this category combine two or more approaches from
	      the previous techniques.
\end{itemize}
Our focus in this paper is on extracting discriminating patterns that represent
time series from each class. The extracted patterns then can be used by
algorithms from the shapelet based technique in order to execute the
classification task.

@@

\section{Related work}
NN-Descent~\cite{NN-Descent} is based on the principle: \textit{A neighbor of
	a neighbor is likely to be a neighbor}. The idea is, given an approximation
graph of the nearest neighbor, then the approximation can be improved,
in an iterative fashion, by exploring the neighbors of the neighbors of each
point. To improve the running time, the authors use local join to avoid
comparing same points many times in the same iteration. They also use
incremental search to avoid comparing points that have been compared in
previous iterations. Also, sampled is used to lower the overhead of local
joins. Finally, random projection trees are used to initialize the graph.

>>>>

\section{Introduction}
Time series classification is similar to traditional classification where the
difference is that the order of the values of the time series is crucial.
The order holds discriminatory features for the time series. The literature
is rich of algorithms for classification, and one way to group these
algorithms is based on the techniques that each algorithm uses to exploit the
discriminatory features suggested by Bagnall et al.~\cite{bake_off}:
\begin{itemize}
	\item Distance based: Classification is based on using distance measures to
	      the raw time series.
	\item Feature based: Global features are extracted and the data is transformed
	      from the time domain to the feature domain spanned by the extracted
	      features, and the classification is done using a standard classifier.
	\item Interval based: Techniques in this family extract one or more intervals,
	      then statistical summaries of these intervals are used as features.
	\item Shapelet based: This technique exploits discriminatory patterns that
	      appear in time series of the same class.
	\item Dictionary based: These algorithms use as features the count of
	      repeating patterns.
	\item Convolution based: Features used are extracted from time series using
	      convolutions and pooling operations.
	\item Deep learning: Classification is done by feeding the data to neural
	      networks
	\item Hybrid: Algorithms in this category combine two or more approaches from
	      the previous techniques.
\end{itemize}
Our focus in this paper is on extracting discriminating patterns, i.e. shapelets
that represent time series from each class. The extracted patterns then can be 
used by algorithms from the shapelet based technique in order to execute the
classification task.

@@

\section{Preliminaries}

\section{Related work}
This~\cite{keogh_shapelet} is where it all started, it has to be here.
This paper~\cite{random_shapelets} uses random shapelet extraction.
This paper~\cite{fss} uses neat tricks select shapelets.
This paper~\cite{learning_shapelets} takes an alternative approach, where 
instead of selecting shapelets it \emph{learns} non existing shapelets.
We should mention the evaluation measures~\cite{alternative_measures}.
We will use Silhouette~\cite{silhouettes} as motivation to exploit neighborhood
structure.

%NN-Descent~\cite{NN-Descent} is based on the principle: \textit{A neighbor of
	%a neighbor is likely to be a neighbor}. The idea is, given an approximation
%graph of the nearest neighbor, then the approximation can be improved,
%in an iterative fashion, by exploring the neighbors of the neighbors of each
%point. To improve the running time, the authors use local join to avoid
%comparing same points many times in the same iteration. They also use
%incremental search to avoid comparing points that have been compared in
%previous iterations. Also, sampled is used to lower the overhead of local
%joins. Finally, random projection trees are used to initialize the graph.
